Clearance Project - 1 - Data Generation

### 2025-03-19 data-raw/ClearanceProject-1-DataRmd.Rmd
Updating data.

cvt_plasma_chems <-  cvt %>% 
    filter(species %in% c("human", "rat"),
           conc_medium_normalized == "plasma") %>%
    pull(analyte_dtxsid)

@@

# save in an .Rdata file
save(target_chems_human, target_chems_rat, 
     human_3compchems, rat_3compchems,
     file = "data-raw/chem_lists.RData")

>>>>

cvt_plasma_chems <-  cvt %>% 
    filter(species %in% c("human", "rat"),
           conc_medium_normalized == "plasma") %>%
    pull(analyte_dtxsid) %>% unique()

@@

# save in an .Rdata file
save(target_chems_human, target_chems_rat, 
     human_3compchems, rat_3compchems,
     cvt_plasma_chems,
     file = "data-raw/chem_lists.RData")
